The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-04-23 Data/BMR/simulations/text.tex
some sim details

%%%%%%%%%%%%%%%%%%%%%%%% Simulation text

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%% Simulation text
We simulated bivariate character evolution on an estimate of 
  phylogeny for 817 mammal species taken from \citep{GenoudIM2018}.
The simulator was written in Python and used version 4.4 of 
  the DendroPy \citep{DendroPy} package.

@@

@article{GenoudIM2018,
author = {Genoud, Michel and Isler, Karin and Martin, Robert D.},
title = {Comparative analyses of basal rate of metabolism in mammals: data selection does matter},
journal = {Biological Reviews},
volume = {93},
number = {1},
pages = {404-438},
keywords = {basal rate of metabolism, BMR, brain, encephalization, allometric scaling, phylogenetic generalized least-squares regression, mammals},
doi = {10.1111/brv.12350},
url = {https://onlinelibrary.wiley.com/doi/abs/10.1111/brv.12350},
eprint = {https://onlinelibrary.wiley.com/doi/pdf/10.1111/brv.12350},
year = {2018}
}

@article{DendroPy,
    author = {Sukumaran, Jeet and Holder, Mark T.},
    title = "{DendroPy: a Python library for phylogenetic computing}",
    journal = {Bioinformatics},
    volume = {26},
    number = {12},
    pages = {1569-1571},
    year = {2010},
    month = {04},
    abstract = "{Summary: DendroPy is a cross-platform library for the Python programming language that provides for object-oriented reading, writing, simulation and manipulation of phylogenetic data, with an emphasis on phylogenetic tree operations. DendroPy uses a splits-hash mapping to perform rapid calculations of tree distances, similarities and shape under various metrics. It contains rich simulation routines to generate trees under a number of different phylogenetic and coalescent models. DendroPy's data simulation and manipulation facilities, in conjunction with its support of a broad range of phylogenetic data formats (NEXUS, Newick, PHYLIP, FASTA, NeXML, etc.), allow it to serve a useful role in various phyloinformatics and phylogeographic pipelines.Availability: The stable release of the library is available for download and automated installation through the Python Package Index site (http://pypi.python.org/pypi/DendroPy), while the active development source code repository is available to the public from GitHub (http://github.com/jeetsukumaran/DendroPy).Contact:jeet@ku.edu}",
    issn = {1367-4803},
    doi = {10.1093/bioinformatics/btq228},
    url = {https://doi.org/10.1093/bioinformatics/btq228},
    eprint = {http://oup.prod.sis.lan/bioinformatics/article-pdf/26/12/1569/809362/btq228.pdf},
}
